master thesis

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological View: Platyhelminthes

      In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
        Table \ref{table:table:percentage loss information subtrees}). This results in a weaker spread of 
        errors. This is reflected in the results from the table \ref{table:phylum leaf nodes states}. 
        There are 18 parasites as input data and only 8 more are predicted. The chordata mostly consist of 
        free-living species, so this seems believable. We started with 99.83~\%  species and 
        predict 99.97~\% species as free-living (including already known nodes). 
        \todo{A few punctual tests give us the following:}

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata \\ 
          Input parasites (green) $\rightarrow$ predicted parasites (white $\rightarrow$ green)}
        \label{fig:ChordataParasites}
      \end{figure}
    %---------------------------------------------------------------------------------------------------

@@

      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 0.1~\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]} \\
      Note:Plythylmintes had less missing information than starting point, see Table \ref{table:percentage loss information subtrees}.

>>>>

      In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
        Table \ref{table:percentage loss information subtrees}). This results in a weaker spread of errors. 
        This is reflected in the results from the table \ref{table:phylum leaf nodes states}. There are 18 
        parasites as input data and only 8 more are predicted. The chordata mostly consist of free-living 
        species, so this seems believable. We started with 99.83~\%  species and predict 99.97~\% species 
        as free-living (including already known nodes). \todo{A few punctual tests give us the following:}

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata \\ 
          Input parasites (green) $\rightarrow$ predicted parasites (white $\rightarrow$ green)}
        \label{fig:ChordataParasites}
      \end{figure}

@@

      Most species of Platyhelminthes (flatworms) are parasites, although there are also free-living, 
        predatory feeding species. These are summarized in the Turbellaria, while the parasites are 
        divided into three other classes \cite{Ax1961}. This also corresponds to our observations. There 
        is one class (Rhabditophora) that contains all but one single exception of free-living species 
        of this phylum, which includes the Turbellaria. \\
      It should be noted, however, that this classification is outdated, as it has been proven that 
        the Turbellaria are not monophyletic. But we will not go into that here. \\
      For the Platyhelminthes we had more state information for the leaf nodes compared to the other 
        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
        0.1~\% free-livings and predicted 0.77~\% as free-living spezies. \\
